\ch{About The Book}

Seeing as we're just starting out right now, there's not much to say yet.
However, we'll be sure to put a few anecdotes in here once we have them!

\s{Contributing}

This book is incomplete.  Ideally, we'd like to provide at least a brief
description of each topic you might encounter as a mathematics undergraduate
student, as well as some highlights of more advanced areas.  We don't know every
area well enough to write a chapter on it, so we're always glad to have guest
contributions.

Apart from writing an introduction to your topic of choice, you can also help by
telling us what you thought of the book, asking about passages that are unclear,
and contributing exercises and solutions.

The best way to get in contact with us is by joining the {\tt \#learnmath}
channel on the Freenode IRC network.  You can use the Web
Client\footnote{\url{http://webchat.freenode.net/?channels=\%23learnmath\&uio=MT11bmRlZmluZWQb1}{}}
if you prefer.  The channel is intended for the entire LearnMath community, so
you're also welcome to ask any other mathematics questions you have.

If IRC isn't your cup of tea, you can always send one of the authors an email.

\s{Collaboration}

We are using GitHub to organise the work we're doing and store our files.  In
our repository there\footnote{\url{https://github.com/learnmath/book}} you can
find the latest version of the book, report any mistakes you find, and propose
changes.

\s{Use and Reuse}

At the moment, we haven't yet decided on how we will license this book.
Whatever we end up doing, we'll make sure you can read the book for free, and
you'll probably be allowed to use it in a classroom setting, too.  Check back
soon for a more detailed account.

