\ch{Introduction}

Mathematics is driven by curiosity, and a good question is one of the most
valuable things you can have. With this book, we hope to give you a basic
familiarity with several fields of mathematics, and inspire you to ask your own
questions about them.

Let's start with an example: suppose you have a rectangle. Can you cut it into
squares that are all the same size?

If you're used to mathematics as it is taught at school, this might not seem
like much of a mathematical question at all; we're not calculating anything, and
we're not solving any equations. It turns out that questions like this, where we
explore what is possible, are some of the most interesting out there.

While we're showing you the various areas of mathematics that we'll use as
inspiration for our questions, we'll show you how to relate these areas to each
other, and give you the tools to do this yourself in the future. We don't intend
to make you an expert in any of these fields, but we hope we'll give you both
the context and the spark of curiosity to look further.


% TODO: Move this elsewhere, it breaks the flow.
\s{Boring stuff}

This section is for people who want to get involved in our community. (Bleh,
right?)

If you like chatting on IRC, come see us in {\tt \#learnmath} on Freenode. If
you don't know what IRC is, or you don't have a client set up, you can connect
through
\link{http://webchat.freenode.net/?channels=\%23learnmath\&uio=MT11bmRlZmluZWQb1}{Freenode's
  webchat}.

\ss{Contributing to this Book}

This book is open-source. You can go to
\link{https://github.com/learnmath/book}{our GitHub page} and see for yourself.
Part of being open-source means you can freely distribute the book, sell it, or
even change it. There are some restrictions, though (see \cref{ss: Licensing} for
details).

Most of them are fairly minor; if, for instance, you are a schoolteacher and
want to use this for your class, you are free to edit it to your liking and
give the modified copy to your students. The only real caveat is that you must
publish your source so others can use it. This may be a problem if you want to
do something such as include more exercises without publishing solutions. If
that is the case, open an issue on the
\link{https://github.com/learnmath/book/issues}{issue tracker} and we'll talk
about granting you an exception to the license.

You are more than welcome to contribute, but please read the
\link{https://github.com/learnmath/book/blob/master/contributing.md}{contributing guide}
first. (Sorry, we know how annoying those are.)

If you notice any errors, don't be shy! Report them in the
\link{https://github.com/learnmath/book/issues}{issue tracker}. If you have any
suggestions for improving this book, post them in the issue tracker too (or bring
them up in the IRC channel).

If you have any questions about this book (or math), feel free to ask in the channel.

\ss{Licensing}

\s{Conventions used in this book}



\s{How to read this book (and how to learn math)}

Now that that's all out of the way, let's talk a little about math. When this
chapter is over, we're going to dive right in to proving a bunch of things you
already know to be true. We feel that without a little explanation, these
proofs may leave you a little lost or confused. We'll save the explanation of
the proofs for later, but right now, we're going to talk about how to actually
learn math, and the proofs are a great example.

Most people's experience with math is through their primary and possibly
secondary education, which is or was a dreary affair in general, and math
probably even moreso, unless you're one of the lucky few. By lucky few, we
don't mean those wizards with a sort of inherent ability to do math--the first
thing you need to know about learning math is that math is for everyone with a
brain--that's you, right? You see, your brain is a pattern recognition engine,
and that's all math is: the study of patterns. Unlike reading or history, your
body comes with a biological imperative to know math. There's some really great
brain studies on the topic, but that's boring, and I said we're already done
with the boring part, so let's move on.

In that last paragraph, we presented what we hold to be the proper answer to
'what is math': the study of patterns. This is completely different from most
people's interaction with math: in primary school, we are taught how to apply
four operations to solve math problems. You're given something about two trains
leaving a station and going different speeds and different directions and yadda
yadda yadda and before you know it your teacher turned everything into a math
problem and it all seemed so forced--a layer on top of what was intuitive, and
made everything complicated. We agree--this is a counterintuitive approach to
math, and it makes math very confusing and disconnected. Math is just the study
of patterns. That is, math is not so much a way to solve a set of problems that 
exist in a sphere apart from what is natural, but a way to understand what's 
going on in the world around us. When you learn math, you should think of it as 
a science--another level of detail in the amazing world we live in.

That's how this book is written. It's written to reflect that math is a single 
unified study. While you're reading it, try to think of how what you're learning
clarifies or refines early material. This is a big deal to us, because one thing
we dislike most about the standard way of learning math is that at some point in 
everyone's math career, they learn they were taught something that wasn't actually
true. We want to avoid that.
